---
toc: false
format:
  html:
    include-before-body: hero-image.html
    sidebar: false
    anchor-sections: false
    css: [theme.css, index.css]
listing:
  id: latest-events
  contents:
    - "events/*/index.qmd"
    - "events/external.yml"
  sort: "date desc"
  template: _event-feed.ejs
  date-format: "YYYY-MM-DD"
  fields: [title, date, categories, host, event-dates]
  sort-ui: false
  filter-ui: false
---

```{r}
#| include: false
source("R/home.R")
ev <- past_events()
unis <- universities()
stats <- network_stats(ev, unis)
number_word <- function(n) if (n <= 10) c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")[n] else n
latest <- Filter(function(u) u$node == stats$latest_node, unis)[[1]]
```

::: {.home-intro .reveal}
[Our mission]{.mission-kicker}

[Facilitating knowledge exchange and connections among development economists based in the Netherlands.]{.mission-statement}

::: {.mission-support}
Our members are researchers from eight participating universities: Erasmus University Rotterdam, Groningen, Nijmegen, Tilburg, UNU-MERIT, Utrecht, VU Amsterdam, and Wageningen. We organize two annual events — a general workshop and one dedicated to PhD students — and we are affiliated to the [European Development Economics Group](https://www.ede-group.org/).
:::
:::

<!-- The network: numbers and the map of member universities -->

::::: {.column-screen .home-network}
:::: {.home-network-inner}

::: {.network-copy .reveal}
[Since `r stats$first_year`]{.section-kicker}

## Our network in numbers {.section-title}

Every year the workshop moves to another member university. The line on the map follows its route, from `r city_of(stats$first_node)` in `r stats$first_year` to `r city_of(stats$latest_node)` in `r stats$latest_year`. Select a university to meet its coordinator.

```{r}
#| echo: false
tags$ul(class = "network-stats",
  tags$li(tags$span(class = "stat-num", `data-count` = stats$workshops, stats$workshops),
          tags$span(class = "stat-label", "annual workshops")),
  tags$li(tags$span(class = "stat-num", `data-count` = stats$phd, stats$phd),
          tags$span(class = "stat-label", "PhD workshops")),
  tags$li(tags$span(class = "stat-num", `data-count` = stats$papers, `data-suffix` = "+", paste0(stats$papers, "+")),
          tags$span(class = "stat-label", "papers presented")),
  tags$li(tags$span(class = "stat-num", `data-count` = stats$universities, stats$universities),
          tags$span(class = "stat-label", "universities"))
)
```

[Based at one of these universities? [Contact your coordinator](members/universities/index.qmd) to join the network.]{.network-join}
:::

::: {.network-visual .reveal}
```{r}
#| echo: false
HTML(paste(readLines("images/network-map.svg", warn = FALSE), collapse = "\n"))
```

```{r}
#| echo: false
# the card starts on the most recent host; the map's script swaps it on hover, focus or tap
div(class = "node-card", `aria-live` = "polite",
  tags$img(class = "node-card-photo", src = latest$photo, alt = ""),
  div(
    tags$p(class = "node-card-uni", latest$university),
    tags$p(class = "node-card-person", latest$coordinator),
    tags$p(class = "node-card-role", latest$role),
    tags$p(class = "node-card-hosted", "Most recent host")
  )
)
network_data(ev, unis)
```
:::

::::
:::::

<!-- Events: the latest three, pulled from events/ -->

::: {.column-screen .home-events .reveal}
::: {.home-events-head}
<div>
[What's on]{.section-kicker}

## Upcoming and recent events {.section-title}
</div>

[All events &rarr;](events/index.qmd){.btn-events}
:::

::: {#latest-events}
:::
:::

<!-- People and moments -->

::::: {.column-screen .home-people}
::: {.home-people-head .reveal}
<div>
[Community]{.section-kicker}

## The people behind the network {.section-title}
</div>

[Meet all members &rarr;](members/members/index.qmd){.btn-events}
:::

```{r}
#| echo: false
photo_strip()
people_strip(n = 14)
```

::: {.home-people-foot}
[Event photos publicly shared by participants.]{.strip-caption}

<button class="strip-toggle" type="button" aria-pressed="false">Pause motion</button>
:::
:::::

<script>
(function () {
  var reduced = window.matchMedia('(prefers-reduced-motion: reduce)').matches;

  // --- the network: count up and draw the route once the section is in view
  var section = document.querySelector('.home-network');
  var map = document.querySelector('.network-map');
  var counters = document.querySelectorAll('.stat-num[data-count]');

  function countUp(el) {
    var target = +el.dataset.count, suffix = el.dataset.suffix || '', start = performance.now();
    (function tick(now) {
      var p = Math.min(1, (now - start) / 1400);
      el.textContent = Math.round(target * (1 - Math.pow(1 - p, 3))) + suffix;
      if (p < 1) requestAnimationFrame(tick);
    })(start);
    // browsers throttle animation frames in background tabs: always land on the real number
    setTimeout(function () { el.textContent = target + suffix; }, 1600);
  }

  if (!reduced && 'IntersectionObserver' in window && section && map) {
    map.classList.add('nm-animate');
    counters.forEach(function (el) { el.textContent = '0' + (el.dataset.suffix || ''); });
    var io = new IntersectionObserver(function (entries) {
      if (!entries.some(function (e) { return e.isIntersecting; })) return;
      io.disconnect();
      map.classList.add('is-drawn');
      counters.forEach(countUp);
    }, { threshold: 0.3 });
    io.observe(section);
  }

  // --- map nodes update the coordinator card
  var data = JSON.parse(document.getElementById('network-data').textContent);
  var card = document.querySelector('.node-card');
  var nodes = document.querySelectorAll('.nm-node');

  function show(id) {
    var u = data[id];
    if (!u) return;
    nodes.forEach(function (n) { n.classList.toggle('is-active', n.dataset.node === id); });
    card.querySelector('.node-card-photo').src = u.photo;
    card.querySelector('.node-card-uni').textContent = u.university;
    card.querySelector('.node-card-person').textContent = u.coordinator;
    card.querySelector('.node-card-role').textContent = u.role;
    card.querySelector('.node-card-hosted').textContent = u.latest ? u.hosted + ' · most recent host' : u.hosted;
  }

  nodes.forEach(function (n) {
    var id = n.dataset.node;
    n.addEventListener('mouseenter', function () { show(id); });
    n.addEventListener('focus', function () { show(id); });
    n.addEventListener('click', function () { show(id); });
    n.addEventListener('keydown', function (e) {
      if (e.key === 'Enter' || e.key === ' ') { e.preventDefault(); show(id); }
    });
  });
  var start = document.querySelector('.nm-node.is-latest');
  if (start) show(start.dataset.node);

  // --- a way to stop the moving strips (and none needed without motion)
  var toggle = document.querySelector('.strip-toggle');
  var people = document.querySelector('.home-people');
  if (toggle && reduced) toggle.hidden = true;
  if (toggle) toggle.addEventListener('click', function () {
    var paused = people.classList.toggle('is-paused');
    toggle.setAttribute('aria-pressed', paused);
    toggle.textContent = paused ? 'Play motion' : 'Pause motion';
  });
})();
</script>
